---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aoc.elf

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg?style=flat-square)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of aoc.elf is to provide helper functions for [Advent of Code](https://adventofcode.com)

## Installation

You can install aoc.elf with:

``` r
remotes::install_github("tanho63/aoc.elf")
```

## Usage

Key functions:

```{r eval = FALSE}
aoc_cookie_set(cookie = "{COOKIE}")
```

You can find the cookie value here https://i.imgur.com/IHEBzAe.png in your network tab. Alternatively set AOC_COOKIE environment variable in .Renviron

```{r eval = FALSE}
aoc_init(day = 2)
```

will create a new RMD template for day two. Can also specify year, path, overwrite, and open.

```{r eval = FALSE}
aoc_get(2)
```

will download inputs for the specified day/year into the path. The template has a chunk with this pre-filled, so you can just run that chunk instead!
